---
title: "Working with data and functions"
output: html_notebook
---

# Exploring the MLB data

```{r}
load("../../data/mlb.RData")
ls()
head(mlb)
mlb$inch2cm <- mlb$height * 2.54

inchToCm <- function(x,d = 2){
  cm <- (x * 2.54) / 100
  round(cm,digits = d)
}
ls()

```

## Questions: 

  - How many observations are in the dataset?
  - Who is the tallest / smallest player?
  - Are players older than 32 significantly heavier than younger players?
  
  
```{r}
# no of observations
nrow(mlb)
mlb[which.max(mlb$height),"Name"]
mlb$old <- mlb$Age > 32
old_players <- mlb[mlb$old,]
young_players <- mlb[!mlb$old,]
t.test(old_players$weight,young_players$weight)
t.test(weight ~ old,data = mlb)
```

## lapply / anonymous function: Who is the average size by position?

1. split the dataset by position to obtain a list
2. run `mean` on the list

```{r}
by_pos <- split(mlb,factor(mlb$Position))
sapply(by_pos,nrow)

# by_pos$Catcher
sizes <- sapply(by_pos,function(x) mean(x$height))
sizes
```

## A custom function: What's the size of these players in centimeters?

```{r}
inchToCm <- function(size_in_inch,meters = T,digits=2){
  out <- size_in_inch * 2.54
  if(meters) out <- round(out/100,digits=2)
  out
}
inchToCm(sizes)
```





